Append_smoothed_results

### 2016-11-22 Code/append_smoothed_results.Rmd
made marginal COD tables

#there are quite a few < 1:
length(dat.clean$total_smoothed_deaths[dat.clean$total_smoothed_deaths < 0.1 & dat.clean$Appended_smoothed == T])
length(dat.clean$total_smoothed_deaths[dat.clean$total_smoothed_deaths < 0.5 & dat.clean$Appended_smoothed == T])
length(dat.clean$total_smoothed_deaths[dat.clean$total_smoothed_deaths < 1 & dat.clean$Appended_smoothed == T])
```

@@

@@

```{r save_specified_files}
save(dat.clean, dat2, BlackWhite, BlackWhiteSmooth, paired.ids, list.age.decomp.tables, list.cod.decomp.tables,
     list.age.decomp.tables5, list.cod.decomp.tables5, list.age.decomp.tables9, list.cod.decomp.tables9,
     list.age.decomp.tables.smoothed, list.cod.decomp.tables.smoothed,
     file = "/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/main_datasets.Rdata")
```

>>>>

#there are quite a few < 1:
length(dat.clean$total_smoothed_deaths[dat.clean$total_smoothed_deaths < 0.1 & dat.clean$Appended_smoothed == T])
length(dat.clean$total_smoothed_deaths[dat.clean$total_smoothed_deaths < 0.5 & dat.clean$Appended_smoothed == T])
length(dat.clean$total_smoothed_deaths[dat.clean$total_smoothed_deaths < 1 & dat.clean$Appended_smoothed == T])

View(dat.clean[dat.clean$total_smoothed_deaths < 1 & dat.clean$Appended_smoothed == T, ])
```

@@

```{r compute_marginal_COD_decomposition}
list.cod.marginal.tables.smoothed <- vector(mode = "list", length = dim(paired.ids)[1])

for(i in 1:dim(paired.ids)[1]) {
    if(list.cod.decomp.tables.smoothed[[i]][1] != "Couldn't compare life tables" & 
       list.cod.decomp.tables.smoothed[[i]][1] != "Encountered age group with no deaths") {

       list.cod.marginal.tables.smoothed[[i]] <- list.cod.decomp.tables.smoothed[[i]] %>% 
                                                  group_by(Cause.of.death) %>% 
                                                  summarise(C_x_COD = sum(C_xi))

    }
}
```

@@

```{r save_specified_files}
save(dat.clean, dat2, BlackWhite, BlackWhiteSmooth, paired.ids, list.age.decomp.tables, list.cod.decomp.tables,
     list.age.decomp.tables5, list.cod.decomp.tables5, list.age.decomp.tables9, list.cod.decomp.tables9,
     list.age.decomp.tables.smoothed, list.cod.decomp.tables.smoothed, list.cod.marginal.tables.smoothed,
     file = "/Users/corinneriddell/Dropbox/BlackWhiteGap/Data/main_datasets.Rdata")
```
